Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
Rewrite paragraph in the conclusion

To choose an appropriate planner for the UAV domain, we have discussed other
existing benchmark domains used in the IPPC\. By looking closely at the domains
we identified some issues with the domains, to make it less interesting for
FF-Replan (in the case of the \textsc{Traffic} domain), of how to make a domain
more interesting for a replanner in the \textsc{Navigation} domain. The UAV
domain seems to have resemblances of the \textsc{Navigation} domain and the
\textsc{SysAdmin} domain.

>>>>

To choose an appropriate planner for our UAV domain, we have analyzed some of
the most important domains in the course of history of probabilistic planners.
The UAV domain seems to have resemblances of the \textsc{Navigation} domain
and the \textsc{SysAdmin} domain. With this knowledge a proposal can be made
for a matching planner.
